On exponential sums arising from the classical doubling method

### 2025-03-20 paper.tex
Typo

\begin{lemma}
\label{lem:indep_geo_conj}
    If $(T,\theta)$ and $(T', \theta)$ are geometrically conjugate, then $$\frac{\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi}}{R_{T,\theta}(1)} = \frac{\dblVirtualJacobiSumScalar{R_{T', \theta'}}{\chi}}{R_{T,\theta}(1)}.$$
\end{lemma}

>>>>

\begin{lemma}
\label{lem:indep_geo_conj}
    If $(T,\theta)$ and $(T', \theta)$ are geometrically conjugate, then $$\frac{\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi}}{R_{T,\theta}(1)} = \frac{\dblVirtualJacobiSumScalar{R_{T', \theta'}}{\chi}}{R_{T',\theta'}(1)}.$$
\end{lemma}
